\textbf{Computational Fuzzy Extractors}

### 2013-02-15 CompFuzzExt.tex
New section 6

%\begin{definition}
%\label{def:unp entropy}
%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
%\[
%\Pr[C(Z) = Y ] \leq 2^{-k}
%.\]
%\end{definition}
%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational secure sketch} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.

\section{Lossless sketch based on \class{LWE}}
\label{sec:fuzzyCompExt}

@@

\begin{theorem}
\label{thm:lossless secure sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure sketch log} shows that a computational secure sketch can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.  A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

\section{\consref{cons:informal construction} with Symbol Fixing Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational secure sketch for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m - \alpha)b$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

@@

\thref{thm:blockLWE} allows us to construct a computational secure sketch from block-fixing sources:

@@

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)n/d+\alpha)b}$.  Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.   There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless secure sketch.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
%\[
%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
%\]
$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{2d+3} \log n)$.
\end{theorem}

\section{Computational Fuzzy Extractors}
In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using a paradigm similar to \lemref{lem:fuzzy ext construction}.  We begin with a formal definition of a computational fuzzy extractor:
\label{sec:comp fuzzy extractors}
\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, s_{rec}, s_{sec}, \epsilon)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\rep( w', P) = R$.  Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

\textbf{Note: }A computational fuzzy extractor can be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).  However, the entropy loss due to error correction may mean there is not be enough remaining bits to run a pseudorandom generator.  Depending on the application, it may be appropriate to make the sketch and/or extractor computational.

Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).  It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.  However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).  
\begin{definition}
An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.  Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
\end{definition}
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
\begin{lemma}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, s_{sec}, s_{sketch}, s_{rec}, t)$-computational secure sketch, and let $\rext:\mathcal{M}\times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
\begin{itemize}
\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
\end{itemize}
\end{lemma}
\begin{proof}
Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
\end{proof}

%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.

>>>>

%\begin{definition}
%\label{def:unp entropy}
%For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
%\[
%\Pr[C(Z) = Y ] \leq 2^{-k}
%.\]
%\end{definition}
%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{noisy computational conductor} is a pair of randomized procedures, sketch (\sketch) and recover (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$ hard with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a noisy computational conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the LWE problem.

\section{Lossless conductor based on \class{LWE}}
\label{sec:fuzzyCompExt}

@@

\begin{theorem}
\label{thm:lossless secure conductor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure conductor log} shows that a noisy computational conductor can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point $B$ and thus providing no information about either $X$ or $W$.  A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

\section{\consref{cons:informal construction} with Symbol Fixing Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a noisy computational conductor for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m - \alpha)b$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

@@

\thref{thm:blockLWE} allows us to construct a noisy computational conductor from block-fixing sources:

@@

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\Fq^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be $\alpha$-symbol fixing source over $\zo^{((c+d)n/d+\alpha)b}$.  Assume GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms.   There is a setting of $q = poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2} |\sketch(W)) = H_\infty(W)$ for %the following parameters:
%\[
%(\zo^{((c+d)n/d+\alpha)b}, \Hoo(W),\Hoo(W), \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)\text{-computational secure sketch}
%\]
$\epsilon = \ngl(n), s_{sec} = \poly(n)$, sketch time $O(n^3\log n)$, and expected recover time $O(n^{2d+3} \log n)$.
\end{theorem}

\section{Computational Fuzzy Extractors}
In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.  We begin with a formal definition of a computational fuzzy extractor:
\label{sec:comp fuzzy extractors}
\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
An $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\rep( w', P) = R$.  %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  
If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
\end{itemize}
We say that $\gen, \rep$ is $(\epsilon, s_{sec})$ hard with error $\delta$.
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

\textbf{Note: }A computational fuzzy extractor can be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).  However, the entropy loss due to error correction may mean there is not be enough remaining bits to run a pseudorandom generator.  Depending on the application, it may be appropriate to make the noise correction procedure and/or extractor computational.

Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
\begin{lemma}
Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.  Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.  Let, $s' = s_{sec}-s_{ext}$, then 
$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
\end{lemma}
%  the same paradigm from 
%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).  It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.  However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).  
%\begin{definition}
%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.  Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
%\end{definition}
%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
%\label{lem:unp extraction} 
%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
%\end{lemma}
We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
\begin{lemma}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-noisy computational conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.  Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.  Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
\end{lemma}
%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
%\begin{itemize}
%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
%\end{itemize}
%\end{lemma}
%\begin{proof}
%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
%\end{proof}
%
%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
